\documentclass[overlapped,line]{res}
\topmargin=-.74in
\oddsidemargin -.5in
\evensidemargin -.5in
\textheight=11in
\textwidth=6.62in
\resumewidth=7.2in
\hoffset=.5in
\sectionwidth=0.5in
\newsectionwidth{0in}
\sectionskip=0.1in

\renewcommand{\sectionfont}{\bf}


\begin{document}

\moveleft.5\hoffset\centerline{\huge\bf Preston H. Carpenter}
\vspace{.2em}

\moveleft.5\hoffset\centerline{email: APragmaticPlace@gmail.com $|$ personal phone: 417-438-7110}
\moveleft.5\hoffset\centerline{linkedin.com/in/timidger $|$ github.com/Timidger $|$ timidger.github.io }
\vspace{1em}

\begin{resume}

\section{\underline{EXPERIENCE}}

\textbf{Amazon Web Services (AWS)} $|$ Seattle, WA\hfill April 2020 - June 2025\\
{\sl Software Engineer II}
\begin{itemize} \itemsep -2pt
	\item Led the migration of the global Amazon Linux
		operating system (OS) release process to Step Functions and Cloud Development Kit
		(CDK) achieving a 94\% speedup from 4 days to 6 hours.
	\item Centralized OS release operations into a
		Python CLI, replacing an ad-hoc AWS web-console workflow.
		Engineers now use this tool instead of relying on tribal knowledge
		and outdated runbooks to release Amazon Linux.
	\item In charge of multiple operating system releases with strict
		deadlines and need-to-know information. Successfully released
		Amazon Linux (AL1, AL2, AL2023, and internal
		versions) in every AWS region and partition (Commercial, China,
		US-Government).
	\item Patched CVEs in critical software packages from upstream and other
		distributions. Was part of the chain of trust for embargo'd
		security patches to critical software packages (e.g.
		Linux kernel, \texttt{sudo}, \texttt{log4j}).
	\item Mentored fellow engineers, fostering their learning \& growth.
		Managed an intern who converted to full-time, and a junior
		engineer who transitioned to a more technical role.
		Mentored other junior engineers, including an engineer that
		switched to a more technical role under my guidance.
	\item Automated manual tasks in a distributed
		system for all AWS regions/partitions with
		Rust, Python, and Bash.
	% ADC?
	% 
\end{itemize}

\textbf{Starry} $|$ Boston, MA\hfill February 2019 - April 2020\\
{\sl System Software Engineer}
\begin{itemize} \itemsep -2pt
    \item Implemented backbone fiber network fail-over with Python and networkd.
    \item Designed and produced SSH-based remote device support system for
	    technicians, using Rust and gRPC.
    \item Wrote Rust and C++ firmware for embedded devices that power Starry
	    internet.
\end{itemize}

\textbf{Google} $|$ Montreal, QC\hfill August 2018 - November 2018\\
{\sl Software Developer Intern}
\begin{itemize} \itemsep -2pt
    \item Implemented a system to detect and remove malignant extensions in the Chrome Cleanup
		Tool in C++.%, a program that secures millions of Chrome installs on Windows computers silently every week
    %\item Expanded reporting metrics and updated privacy policy to facilitate
    %unwanted extension fingerprinting.
\end{itemize}

\textbf{Microsoft} $|$ Redmond, WA\hfill May 2018 \--- July 2018\\
{\sl Software Engineer Intern}
\begin{itemize} \itemsep -2pt
	\item Developed a SKU document analyzer and reporting tool for Azure's
		hardware engineers in C\# and HTML.
	%\item Collaborated with other teams to standardize external OEM and
	%	internal datacenter documents for automation.
	%\item Streamlined the configuration program for a boot loader used in
	%	datacenters to be more user friendly.
\end{itemize}

\textbf{Intuit} $|$ San Diego, CA\hfill July 2017 \--- December 2017\\
{\sl Software Engineer Co-op}
\begin{itemize} \itemsep -2pt
	\item Java backend developer on ``machine learning as a service''
		product that powers Mint and Turbo data insights.
	\item Eliminated manual deployment/testing by setting up automated
      continuous integration and deployment in AWS.
	%\item Won the internal ``Codechella'' hackathon by extending the
	%	intranet website to include skills and project search.
\end{itemize}

\textbf{Kinto Care} $|$ Boston, MA\hfill July 2016 \--- January 2017\\
{\sl Full Stack Engineer Co-op}
\begin{itemize} \itemsep -2pt
	\item Developed flagship cross-platform phone app using Javascript with
		React and Cordova.
	\item Integrated and expanded back-end API powered by Flask and
		Postgres.
	%\item Contributed to key design decisions through service research and
    %  weekly Agile sprint meetings
\end{itemize}

\textbf{Beechwood Software} $|$ Boston, MA \hfill January 2017 \--- July 2017\\
{\sl Software Engineer Intern} \hfill November 2015 \--- July 2016
\begin{itemize}  \itemsep -2pt
	\item Contributed C++ to open-source 
		Alljoyn framework in collaboration with Allseen Alliance and
		Linux Foundation.
	%\item Devised smoothing algorithms to calculate distance between a wide range of different quality bluetooth devices
	%\item Assembled and tested the prototype presented at CES in Las Vegas using Rasberry Pis and Nest thermostats.
\end{itemize}
\vspace{-1em}
\noindent\makebox[7.15in]{\rule{7.15in}{0.4pt}}

\section{\underline{PROJECTS}}
\textbf{Way Cooler (Wayland Window Manager)}
\begin{itemize}  \itemsep -2pt
	\item Independently created tiling Wayland window manager with 6,000+
		downloads and 2,000+ stars on Github.
	\item Designed a programmable interface using Lua that extends
      a basic compositor core in Rust.
\end{itemize}

\section {\underline{COMPUTER KNOWLEDGE}}
{\textbf{Languages}: \hskip 1.4em Python, Rust, Go, Java, Javascript, Typescript, C, C++, Bash, Lua \\
\textbf{Technologies}: \hskip 0.3em AWS, CDK, gRPC, Protobuf, NGINX, systemd, Git, 
Wayland, Docker, Flask, Postgres
\vspace{-.7em}
}

% load-bearing
\noindent\makebox[7.15in]{\rule{7.15in}{0.4pt}}

\section{\underline{EDUCATION}} 
 \textbf{Northeastern University} $|$ Boston, MA \hfill September 2014 \--- May 2019 \\
{\sl Bachelor of Science in Computer Science} \\
Relevant Courses: \hskip 1em Compilers, Computer Systems, Programming Languages, \\
\strut\hskip 9.25em Networks and Distributed Systems, Algorithms and Data,
Systems Security
\\
\strut
TA'd Intro to Fundamentals of Computer Science for 4 years, Head TA for
Programming Languages in 2018

%\textbf{wlc-rs, wlroots-rs (Safe Rust bindings to C Wayland libraries)} \hfill October 2017 \--- April 2019
%\begin{itemize} \itemsep -2pt
%  \item Designed and implemented a safe interface to wlc and wlroots (its successor)
%  \item Programmed basic proof-of-concept compositors in 100\% safe Rust,
%    including old versions of Way Cooler.
%    \item Thoroughly explored the design space for designing an ergonomic \&
%      safe API around a complicated C library.
%\end{itemize}

%\textbf{AutoWikiaBot (Reddit bot)} \hfill
%\begin{itemize}  \itemsep -2pt
%       \item Developed a Reddit bot in Python to post summaries of Wikia articles that other users linked
%       \item Configured and managed a server running Linux/Debian hosting the bot remotely using SSH
%       \item Adapted a popular Python Wikipedia library to work for Wikia links
%\end{itemize}

\end{resume}
%\vspace{.1em}
%\moveleft.5\hoffset\centerline{\textbf{Hobbies}: hiking, cat dad, captain of
%kickball team}
\end{document}
